Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
S: Piloting

>>>>

% Make change necessary

Spayd [P49] describes that senior management pushed hard on a mandate to have
deliveries every 90 days. The mandate made change necessary, and while the
strong pressure did not promote agile practices in every case the drive for
change was perceived good in general [P49].

\subsubsection{Create a positive start by piloting}

% Have a successful pilot first

The agile model was usually tried out in the organization before rolling it out
on a general level. Having a pilot project was reported as a significant success
factor in several cases [P3, P9, P38].
The pilot project gave proof that the agile model would be suitable for the
organization and the general acceptance of agile was increased [P3, 17].
The pilot also cleared disbeliefs of the suitability of agile for large
organizations, and created acceptance for both development and management [P31,
P36].

Pilots were especially important for gaining management acceptance. Cases
reported that management gave approval for agile methods only after seeing
successful pilots [P14, P47]. Prokhorenko [P39] also describes that seeing the
example of successful pilots will make managers from other departments eager to
try the new method, and thus help to spread the use of it.
